The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
Updates from ShareLaTeX

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}

\subsection{Profit}

@@

 To find out, we compared the actual Priority to the Number of Comments. Figure n shows this as a box plot. The higher the priority, the more the comment. However, you can see that there are too many outliers and that the data is distributed asymmetrically. This is because the number of comments follows a log distribution. So we applied the logarithmic function to the number of commands and then we compared it again. This is shown in Figure n+1.

As Figure shows, Priority and Member of Comments have a linear relationship. Unlike Priority, Number of segments has a constant distribution of values and various values by requirement. Number of Comments is better than Priority to apply the actual search-based algorithm.

@@

>>>>

\textbf{RQ2}. \textit{Could we estimate COST from Bugzilla without Forward Looking?}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplotraw.png}
    \caption{Priority-number of comments}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\linewidth}
    \includegraphics[width=\linewidth]{images/boxplot.png}
    \caption{Priority-Log(number of comments)}
  \end{subfigure}
  \caption{The same cup of coffee. Two times.}
  \label{fig:priority_comments}
\end{figure*}
\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ec.png}
    \caption{Eclipse}
  \end{subfigure}
  \begin{subfigure}[b]{0.9\linewidth}
    \includegraphics[width=\linewidth]{images/chart_ff.png}
    \caption{Firefox}
  \end{subfigure}
  \caption{Average Time cost at 2016 and 2017 per components}
  \label{fig:time_cost}
\end{figure*}
\subsection{Profit}

@@

 To find out, we compared the actual Priority to the Number of Comments. Figure 1.(a) shows this as a box plot. The higher the priority, the more the comment. However, you can see that there are too many outliers and that the data is distributed asymmetrically. This is because the number of comments follows a log distribution. So we applied the logarithmic function to the number of commands and then we compared it again. This is shown in Figure 1.(b)

As Figure 1.(b) shows, Priority and Member of Comments have a linear relationship. Unlike Priority, Number of segments has a constant distribution of values and various values by requirement. Number of Comments is better than Priority to apply the actual search-based algorithm.

@@

 Unlike Profit, the Cost was a very difficult task to figure out the actual prediction. In fact, it's very difficult for a product manager to calculate the time cost of a particular requirement, and the developers working on the actual task are just guessing how much time they'll take. 
 So we defined the Cost as:

Cost: Average resolution time for the requirements of the same component as the previous year

Bugzilla's repositories are divided into each component. We assumed that the average time it takes to fix the bug for each component would be a constant in next year. Therefore, We concluded that the average bug modification time for each component in 2017 would not be much different from 2016. So the Cost of each requirement was used as a prediction index for the average Cost of that component in 2016.
